Cosmological constraints from the redshift dependence of the volume effect using the galaxy 2-point correlation function across the line-of-sight

### 2017-04-29 draft/draft3.3.tex
updates

\begin{abstract}
We develop a methodology to use the redshift dependence of the galaxy 2-point correlation function across the line-of-sight (2pCF), $\xi(r_{\bot})$, as a probe of cosmological parameters. 
The positions of galaxies in comoving Cartesian space varies under different cosmological parameter choices, 
inducing a {\it redshift-dependent scaling} in the galaxy distribution. 
This geometrical distortion can be observed as a redshift-dependent rescaling in the measured $\xi(r_{\bot})$. 
We test this methodology using a sample of 1.75 billion mock galaxies at redshifts 0, 0.5, 1, 1.5, 2, 
drawn from the Horizon Run 4 N-body simulation.
The shape of $\xi(r_{\bot})$ can exhibit a significant redshift evolution when the galaxy sample is 
analyzed under a cosmology differing from the true, simulated one. 
Other contributions, including the gravitational growth of structure, 
galaxy bias, and the redshift space distortions, 
do not produce large redshift evolution in the shape. 
We show that one can make use of this geometrical distortion to constrain the values of 
cosmological parameters governing the expansion history of the universe. 
This method could be applicable to future large scale structure surveys, 
especially photometric surveys such as DES, LSST, to derive tight cosmological constraints. 
This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016} 
as a strategy to constrain cosmological parameters using redshift-invariant physical quantities.
%We propose to use the redshift dependence of the galaxy 2-point correlation function across the line-of-sight (2pCF), $\xi(r_{\bot})$, to constrain cosmological parameters.
%When an incorrect set of cosmological parameters is assumed for transforming galaxy redshifts to comoving distances, 
%it produces {\it redshift-dependent mis-scaling} in the galaxy distribution.
%As a result, we observe a redshift-dependent rescaling in the measured $\xi(r_{\bot})$.
%We test this idea using a sample of 1.75 billion mock galaxies at redshifts 0, 0.5, 1, 1.5, 2,
%drawn from the Horizon Run 4 N-body simulation.
%The shape of $\xi(r_{\bot})$ exhibits redshift evolution when the adopted cosmology is wrong,
% mock galaxy catalogues having hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2.
%while the other effects, including the gravitational growth of structure,
%galaxy bias, and the redshift space distortions, do not produce large redshift evolution in the shape.
%Analyzing the 2pCF shape on scales $20  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
%we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
%We show that one can make use of this fact to constrain the values of cosmological parameters governing the 
%expansion history of the universe.
%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
%This method could be applicable to future large scale structure surveys, 
%especially photometric surveys such as DES, LSST, 
%to derive tight cosmological constraints.
%This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
%as a strategy to constrain cosmological parameters using redshift-invariant physical quantities.
%They are all powerful in constraining cosmology and have many merits,
%e.g., they are less affected by the systematic effects induced by non-linear clustering or RSD,
%they do not require accurate modeling of galaxy clustering,
%and are applicable on relatively small clustering scales.
\end{abstract}

@@

In this paper we continue our exploration of redshift invariant galaxy clustering 
and present a new method for constraining cosmology using the redshift evolution of 
the galaxy two-point correlation function (2pCF) across the line-of-sight, $\xi(r_{\bot})$. 
An incorrect choice of cosmology results in {\it redshift-dependent scaling} of the galaxy distribution. 
This, in turn, results in a significant redshift evolution in the shape of $\xi(r_{\bot})$.
Of course the correlation function has other contributions factors that may induce redshift evolution, 
such as the gravitational growth of structure, galaxy bias, and redshift space distortions. 
However we find that these other contributions do not produce large redshift evolution in the shape of $\xi(r_{\bot})$. 
We test this methodology using a sample of 1.75 billion mock galaxies at redshifts 0, 0.5, 1, 1.5, 2, drawn from the Horizon Run (HR) 4 N-body simulation.

@@

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{fig1_a.eps}
   \includegraphics[height=8.5cm]{fig1_b.eps}
   }
   \caption{\label{fig_xyquan}
   A description of how incorrectly assumed cosmologies can distort the interpretation of observation,
   assuming $\Omega_m=0.26,w=-1$ is the true cosmology. 
   Left panel shows a series of five regular squares, measured by an observer at the origin.
   Their true positions and shapes are plotted in blue dashed lines.
   When the observer adopts incorrect cosmologies when computing distances from redshifts and infering the positions and shapes of the squares,
   they obtain distorted shapes (red solid lines).
   Right panel shows the redshift evolution of the wrongly estimated angular diameter distance (divided by the correct value).
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

%Considering we are Let us consider an object in the universe with certain size and shape.
%Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
In this section we briefly introduce the scaling effect caused by incorrectly assumed cosmological parameters.
A more detailed description has been provided in \cite{Li2014,Li2015,Li2016}.

@@

An illustration is provided in the left panels of Figure \ref{fig_xyquan}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present matter ratio $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute a series of perfect squares at distances ranging from 500 Mpc/h to 3\,000 Mpc/h,
and an observer located at the origin were to measure their redshifts and infer the sizes of the squares
using the distance-redshift relations of four incorrect cosmologies
\begin{eqnarray}
 & &{\rm (i)}.\ \Omega_m=0.40,\ w=-1.0, \nonumber \\ 
 & &{\rm (ii)}.\ \Omega_m=0.15,\ w=-1.0, \nonumber\\ \noindent
 & &{\rm (iii)}.\ \Omega_m=0.26,\ w=-0.5,\nonumber\\ \noindent
 & &{\rm (iv)}.\ \Omega_m=0.26,\ w=-1.5,  \nonumber \noindent 
\end{eqnarray}
then the shapes of the squares would appear distorted (AP effect),
and their sizes would be wrongly estimated (volume effect).
Cosmological models (i,iii) result in compressed volume elements (in both angular and LOS directions),
and the degree of compression increases with increasing distance;
the situation is opposite for the other two cosmologies.

@@

In sum, as a consequence of incorrect cosmologies 
the size of objects is mis-estimated and the magnitude of mis-estimation depends on the redshift.
We use the galaxy 2pCF across the line-of-sight to probe the mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.

@@

We test the method using the mock galaxy samples produced by the Horizon Run 4  (HR4) N-body simulation \citep{hr4,hong2016}.

HR4 was made within a cube of volume $({3.15}\ h^{-1}\rm Gpc)^3$ using  $6300^3$ particles with mass $m_p\simeq 9 \times 10^9 \hMsun$.
The simulation adopted the second order Lagrangian perturbation theory (2LPT) initial conditions at $z_{i}=100$
and a WMAP5 cosmology $(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96) \citep{komatsu 2011}.
%The particle mass is $\simeq m_{p} \simeq 9.02 \times 10^9 \hMsun$.
%This starting redshift, combined  with 2LPT initial conditions, ensures an accurate mass function and power spectrum \citep{2014NewA...30...79L}.

@@

The resulting mock galaxies were found to reproduce the 2pCF of the SDSS DR7 volume-limited galaxy sample \citep{zehavi2011} very well.
The mock galaxies shows a similar finger of god (FOG) feature \citep{FOG} as the observation.
The projected 2pCF of the mock and observational samples agree within 1$\sigma$ CL
on scales greater than 1 ${h^{-1}}$Mpc.

%As will be introduced in the next section, 
%The output of HR4 simulation includes one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc 
%and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
We take the snapshot data of the mock galaxies at $z=0,0.5,1,1.5,2$.
%We require subhalos to have at least 30 member particles, 
%so the minimal mass of galaxies is $\simeq m_{p} \simeq 2.7 \times 10^{11} \hMsun$.
Setting a minimal halo mass of $3\times 10^{11} \hMsun$, 
%$4.57\times 10^8$, $4.06\times 10^8$, $3.52\times 10^8$, $3.06\times 10^8$ and $2.28 \times 10^8$ mock galaxies,
we select 457, 406, 352, 306 and 228 million mock galaxies at the five redshifts,
corresponding to a number density of 
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
1.46, 1.30, 1.13, 0.98 and 0.73 in units of $ 10^{-2} h^{3} \rm Mpc^{-3}$
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
respectively.
The total number of galaxies is 1.75 billion.
Applying a uniform mass cut, at higher redshift we obtained a smaller number of galaxies with {\it larger bias}.

As an illustration, Figure \ref{fig_scatter} displays the 2D distribution of a subsample of mock galaxies in five redshifts,
with $x$, $y$ coordinates computed using the ``correct'' cosmological parameters $\Omega_m=0.26,\ w=-1$ (left panels) 
and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$ (right panels), respectively.

When the correct cosmology is adopted the cosmic scale is correctly estimated,
the main factor leads to redshift evolution of galaxy distribution is the gravitational growth of structure.
With decreasing redshift, we clearly see the clusters and filaments form and grow.
On the other hand, when the wrong cosmology is adopted, there is an artificial scaling of distances in the constructed map.
The separations among galaxies are over-estimated by 
$25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
leading to a clear redshift evolution of sizes of structures.

The growth of structure increases the clustering and results in more compact structures,
while the volume effect maintains the clustering pattern and uniformly re-scales structures on all scales.
The imprint of each of these effects on the large scale structure is different and should be distinguishable.
In the following section we show that they affect $\xi(r_{\bot})$ measurements in different ways, 
and thus can be easily separated.

@@

\begin{figure*}
   \centering{
   %\includegraphics[height=5.9cm]{fig8_0.eps}
   %\includegraphics[height=5.9cm]{fig8_wrongcos_0.eps}
   %\includegraphics[width=16cm]{fig2.eps}
   %\includegraphics[width=16cm,natwidth=8,natheight=14]{fig2.pdf}
   \includegraphics[width=16cm]{fig2_0.eps}
   }
   \caption{\label{fig_scatter}
  The 2D distribution of a $260\times130\times105 (h^{-1}{\rm Mpc})^3$ subsample of HR4 mock galaxies, 
  at redshifts 0.5, 1, 1.5 and 2.
  Left and right panels show the $x$, $y$ coordinates computed using the ``correct'' parameters $\Omega_m=0.26,\ w=-1$ 
  and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$, respectively.
  The growth of structure strengths the clustering and make structures more compact at lower redshift.
  When the wrong cosmology is adopted, the comoving distances are mis-scaled and over-estimated by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$, respectively,  leading to a clear redshift evolution of the sizes of structures.
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

We use the 2pCF across the line-of-sight as a statistical tool to probe the volume effect.
The galaxy 2pCF as a function of galaxy separation perpendicular to the LOS, $\xi(r_\perp)$, is computed for snapshot data of mock galaxies at redshifts 0.5, 1, 1.5 and 2.
We adopt the Landy-Szalay estimator~\citep{1993ApJ...412...64L},
\begin{equation}
\xi(r_\perp)=\frac{DD-2DR+RR}{RR}\ ,
\end{equation}
where $DD$ is the number of galaxy--galaxy pairs, 
$DR$ the number of galaxy-random pairs, 
and $RR$ is the number of random--random pairs, 
all separated by a distance defined by $r_\perp\pm\Delta_{r_\perp}$ where we choose $\Delta_{r_\perp}=1h^{-1}\rm Mpc$.
The random catalogue consists of unclustered points uniformly distributed in the same space as the simulated data. 
In an effort to reduce the statistical variance of the estimator, we use 50 times as many random points as we have galaxies.

@@

\subsection{Galaxy 2pCF across the line-of-sight: at different redshifts}\label{sec_2pCF_diffz}

\begin{figure*}
   \centering{
%   \includegraphics[width=18cm]{fig9_0.eps}
%   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
 %   \includegraphics[width=18cm]{fig3.eps}
%    \includegraphics[width=18cm]{fig3_b.eps}
    \includegraphics[width=2\columnwidth]{fig3.eps}
    \includegraphics[width=2\columnwidth]{fig3_b.eps}
   }
   \caption{\label{fig_diffz}
  The 2pCF across the line-of-sight, $\xi_{r_\perp}$ (left panels), the shape of $\hat{\xi}_{r_\perp}$ (middle panels),
  and the evolution with respect to the $z=0$ value, $\hat{\xi}_{r_{\perp}}(z=z_i) - \hat{\xi}_{r_{\perp}}(z=0)$ (right panels). 
  Upper panels show that in the correct cosmology the redshift evolution of the shape of 2pCF is rather small regardless of the large redshfit evolution of the amplitude, 
  whereas the lower panels show that, in a wrong cosmology $\Omega_m = 0.05,w=-1.5$, the redshift evolution of $\hat{\xi}_{r_\perp}$ is very significant.
   }
\end{figure*}

The upper-left panel of Figure \ref{fig_diffz} displays the 2pCF across the line-of-sight measured from HR4 mock galaxies. % (multiplied by scale $r$) in the five snapshot.
We multiply $\xi$ by the separation $r_\perp$ to obtain a similar statistical uncertainty on all scales.
For convenience we will use the denotation
\begin{equation}
 \xi_{r_{\perp}} \equiv r_{\perp} \xi.
\end{equation}

@@

In the upper-middle panel, the overlapping of $\hat\xi_{r_{\perp}}$
clearly show the minimal redshift evolution of the shape.
In the upper-right panel, 
we further show the residual evolution at high redshifts 
with respect to $z=0$.
There is only 1-4\% enhancement 
at $r<10h^{-1}\rm Mpc$,
and $<1.5\%$ suppression at $r>25 h^{-1}\rm Mpc$.
The trend is monotonic with redshift.

@@

\subsection{Galaxy 2pCF across the line-of-sight: cosmological effect }

The 2pCF across the line-of-sight for galaxy positions constructed in a wrongly assumed cosmology $\Omega_m=0.05,\ w=-1.5$
is displayed in the lower panels of Figure \ref{fig_diffz}.
The mis-scaling uniformly shifts the clustering pattern on all scales, 
leading to a biased $\hat \xi_{r_\perp}$, which is 
related with the true $\hat \xi$ as
\begin{equation}
 \hat \xi_{r_\perp,\rm wrong}(r) = \hat \xi_{r_\perp, \rm correct}(\alpha_{\perp} r),
\end{equation}
a simple consequence of the fact that the clustering pattern at scale $r$ is rescaled to $\alpha_{\perp} r$.

@@

The mis-scaling not only changes the shape of the 2pCF but also changes the value of $ \xi_{r_\perp}$. %The amplitude of $r_\perp\xi$ is amplified due to the stretch of scale.
As is shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
the higher the redshift, the greater the enhancement
\footnote{The value of $\xi$ is not affected by the mis-scaling. 
But since we are using $r_\perp\xi$ rather than $\xi$, the y-axis values are affected. 
For a 20\% up-rescaling, the peak value of $r_\perp\xi$ is also increased by 20\%.}.%the amplitude monotonically increases as a function of redshift.

@@

The galaxy peculiar velocity contaminates the observed redshift and distorts 
the inferred galaxy radial position.
It is the major systematic in our previous works \citep{Li2014,Li2015,Li2016}
of statistical analysis on the 3D galaxy distribution.

The effect of RSD is much milder in this work. 
The angular positions of galaxies are not shifted by RSD at all;
the only effect of RSD enter in the procedure of 
splitting galaxies into redshift shells.
The galaxies observed in a survey are split into shells of subsamples, 
with different redshift ranges. This allows us to obtain 2pCF measurement at various redshifts.
RSD distorts the galaxy redshift and as a result some galaxies 
(especially those close to the boundaries of shells) are assigned to the wrong redshift shells.

@@

We vary the mass cut and check the effect of galaxy bias on $\hat \xi_{r_\perp}$.
The second row of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3150\times3150\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
Four values of minimal mass limits, $3\times 10^{11} M_{\odot}$, $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$,
are imposed to create samples with different galaxy biases.
The measured 2pCF across the line-of-sight are displayed.

>>>>

\begin{abstract}
We develop a methodology to use the redshift dependence of the galaxy 2-point correlation function (2pCF) across the line-of-sight, $\xi(r_{\bot})$, as a probe of cosmological parameters. 
The positions of galaxies in comoving Cartesian space varies under different cosmological parameter choices, 
inducing a {\it redshift-dependent scaling} in the galaxy distribution. 
This geometrical distortion can be observed as a redshift-dependent rescaling in the measured $\xi(r_{\bot})$. 
We test this methodology using a sample of 1.75 billion mock galaxies at redshifts 0, 0.5, 1, 1.5, 2, 
drawn from the Horizon Run 4 N-body simulation.
The shape of $\xi(r_{\bot})$ can exhibit a significant redshift evolution when the galaxy sample is 
analyzed under a cosmology differing from the true, simulated one. 
Other contributions, including the gravitational growth of structure, 
galaxy bias, and the redshift space distortions, 
do not produce large redshift evolution in the shape. 
We show that one can make use of this geometrical distortion to constrain the values of 
cosmological parameters governing the expansion history of the universe. 
This method could be applicable to future large scale structure surveys, 
especially photometric surveys such as DES, LSST, to derive tight cosmological constraints. 
This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016} 
as a strategy to constrain cosmological parameters using redshift-invariant physical quantities.
%We propose to use the redshift dependence of the galaxy 2-point correlation function across the line-of-sight (2pCF), $\xi(r_{\bot})$, to constrain cosmological parameters.
%When an incorrect set of cosmological parameters is assumed for transforming galaxy redshifts to comoving distances, 
%it produces {\it redshift-dependent mis-scaling} in the galaxy distribution.
%As a result, we observe a redshift-dependent rescaling in the measured $\xi(r_{\bot})$.
%We test this idea using a sample of 1.75 billion mock galaxies at redshifts 0, 0.5, 1, 1.5, 2,
%drawn from the Horizon Run 4 N-body simulation.
%The shape of $\xi(r_{\bot})$ exhibits redshift evolution when the adopted cosmology is wrong,
% mock galaxy catalogues having hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2.
%while the other effects, including the gravitational growth of structure,
%galaxy bias, and the redshift space distortions, do not produce large redshift evolution in the shape.
%Analyzing the 2pCF shape on scales $20  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
%we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
%We show that one can make use of this fact to constrain the values of cosmological parameters governing the 
%expansion history of the universe.
%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
%This method could be applicable to future large scale structure surveys, 
%especially photometric surveys such as DES, LSST, 
%to derive tight cosmological constraints.
%This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
%as a strategy to constrain cosmological parameters using redshift-invariant physical quantities.
%They are all powerful in constraining cosmology and have many merits,
%e.g., they are less affected by the systematic effects induced by non-linear clustering or RSD,
%they do not require accurate modeling of galaxy clustering,
%and are applicable on relatively small clustering scales.
\end{abstract}

@@

In this paper we continue our exploration of redshift invariant galaxy clustering 
and present a new method for constraining cosmology using the redshift evolution of 
the galaxy two-point correlation function (2pCF) across the line-of-sight (LOS), $\xi(r_{\bot})$. 
An incorrect choice of cosmology results in {\it redshift-dependent scaling} of the galaxy distribution. 
This, in turn, results in a significant redshift evolution in the shape of $\xi(r_{\bot})$.
Of course the correlation function has other contributions factors that may induce redshift evolution, 
such as the gravitational growth of structure, galaxy bias, and redshift space distortions. 
However we find that these other contributions do not produce large redshift evolution in the shape of $\xi(r_{\bot})$. 
We test this methodology using a sample of 1.75 billion mock galaxies at redshifts 0, 0.5, 1, 1.5, 2, drawn from the Horizon Run (HR) 4 N-body simulation.

@@

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{fig1_a.eps}
   \includegraphics[height=8.5cm]{fig1_b.eps}
   }
   \caption{\label{fig_xyquan}
   An illustrative example of how incorrectly assumed cosmologies can distort a distribution of points,
   assuming $\Omega_m=0.26,w=-1$ is the true cosmology. 
   Left panel shows a series of five regular squares, measured by an observer at the origin.
   Their true positions and shapes are plotted as blue dashed lines.
   When the observer adopts incorrect cosmologies when computing distances from redshifts and inferring the positions and shapes of the squares,
   they obtain distorted shapes (red solid lines).
   Right panel shows the redshift evolution of the wrongly estimated angular diameter distance (divided by the correct value).
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

%Considering we are Let us consider an object in the universe with certain size and shape.
%Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
In this section we briefly discuss the scaling effect in the galaxy clustering statistics caused by assuming incorrect cosmological parameters. A more detailed description can be found in \cite{Li2014,Li2015,Li2016}.

@@

An illustration is provided in the left panels of Figure \ref{fig_xyquan}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present matter ratio $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute a series of perfect squares at distances ranging from 500 Mpc/h to 3\,000 Mpc/h,
and an observer located at the origin were to measure their redshifts and infer the sizes of the squares
using the distance-redshift relations of four incorrect cosmologies
\begin{eqnarray}
 & &{\rm (i)}.\ \Omega_m=0.40,\ w=-1.0, \nonumber \\ 
 & &{\rm (ii)}.\ \Omega_m=0.15,\ w=-1.0, \nonumber\\ \noindent
 & &{\rm (iii)}.\ \Omega_m=0.26,\ w=-0.5,\nonumber\\ \noindent
 & &{\rm (iv)}.\ \Omega_m=0.26,\ w=-1.5,  \nonumber \noindent 
\end{eqnarray}
then the shapes of the squares would appear distorted (AP effect),
and their sizes would be wrongly estimated (volume effect).
Cosmological models (i,iii) result in compressed volume elements (in both the angular and LOS directions),
and the degree of compression increases with increasing distance;
the situation is opposite for the other two cosmologies.

@@

In summary, as a consequence of incorrectly assumed cosmologies 
the size of objects is mis-estimated and the magnitude of mis-estimation depends on the redshift.
We thus use the galaxy 2pCF across the LOS to probe the mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.

@@

We test the method using the mock galaxies produced by the Horizon Run 4  (HR4) N-body simulation \citep{hr4,hong2016}.

HR4 was made in a $({3.15}\ h^{-1}\rm Gpc)^3$ cube using  $6300^3$ particles with mass $m_p\simeq 9 \times 10^9 \hMsun$.
The simulation adopted the second order Lagrangian perturbation theory (2LPT) initial conditions at $z_{i}=100$
and a WMAP5 cosmology $(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96) \citep{komatsu 2011}.
%The particle mass is $\simeq m_{p} \simeq 9.02 \times 10^9 \hMsun$.
%This starting redshift, combined  with 2LPT initial conditions, ensures an accurate mass function and power spectrum \citep{2014NewA...30...79L}.

@@

The resulting mock galaxies were found to well reproduce the 2pCF of the volume-limited galaxy sample from Sloan Digital Sky Survey Data Release 7 (SDSS DR7) \citep{zehavi2011}.
The mock galaxies shows a similar finger of god (FOG) feature \citep{FOG} as the observation.
The projected 2pCF of the mock and observational samples agree within 1$\sigma$ CL
on scales greater than 1 ${h^{-1}}$Mpc.

%As will be introduced in the next section, 
%The output of HR4 simulation includes one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc 
%and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
In this analysis, we use five snapshots of mock galaxies at $z=0,0.5,1,1.5,2$.
%We require subhalos to have at least 30 member particles, 
%so the minimal mass of galaxies is $\simeq m_{p} \simeq 2.7 \times 10^{11} \hMsun$.
Setting a minimal halo mass of $3\times 10^{11} \hMsun$, 
%$4.57\times 10^8$, $4.06\times 10^8$, $3.52\times 10^8$, $3.06\times 10^8$ and $2.28 \times 10^8$ mock galaxies,
we select 457, 406, 352, 306 and 228 million mock galaxies at the five redshifts,
corresponding to a number density of 
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
1.46, 1.30, 1.13, 0.98 and 0.73 in units of $ 10^{-2} h^{3} \rm Mpc^{-3}$
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
respectively.
At higher redshift, we have smaller number of galaxies, with a {\it larger bias}.
The total number of galaxies is 1.75 billion.

As an illustration, Figure \ref{fig_scatter} displays a subsample of galaxies at the five redshifts.
Their $x$, $y$ coordinates are computed using two sets of cosmological parameters,
the ``correct'' cosmology $\Omega_m=0.26,\ w=-1$ (left panels),
and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$ (right panels), respectively.

When the correct cosmology is adopted, the cosmic scale is correctly estimated,
and the main factor for the redshift evolution of galaxy distribution is the gravitational growth of structure.
With decreasing redshift, the clusters and filaments form and grow.
On the other hand, the wrong cosmology leads to an artificial scaling of distance.
The separations among galaxies are over-estimated by 
$25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
causing a clear redshift evolution of the sizes of structures.

The growth of structure increases the clustering and results in more compact structures,
while the volume effect maintains the clustering pattern and uniformly re-scales structures on all scales.
Their imprints are different.
In the next section, we show that they affect $\xi(r_{\bot})$ measurements in different manners, 
and thus can be easily separated.

@@

\begin{figure*}
   \centering{
   %\includegraphics[height=5.9cm]{fig8_0.eps}
   %\includegraphics[height=5.9cm]{fig8_wrongcos_0.eps}
   %\includegraphics[width=16cm]{fig2.eps}
   %\includegraphics[width=16cm,natwidth=8,natheight=14]{fig2.pdf}
   \includegraphics[width=16cm]{fig2_0.eps}
   }
   \caption{\label{fig_scatter}
  $x$, $y$ coordinates of a $260\times130\times105 (h^{-1}{\rm Mpc})^3$ subsample of HR4 galaxies, 
  at redshifts 0.5, 1, 1.5 and 2.
  Left and right panels show the coordinates computed using the ``correct'' parameters $\Omega_m=0.26,\ w=-1$ 
  and a wrong cosmology $\Omega_m=0.05,\ w=-1.5$, respectively.
  The growth of structure strengths the clustering and make structures more compact at lower redshift.
  When the wrong cosmology is adopted, the comoving distances are upscaled by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1,1.5,2$, 
  respectively, leading to a {\it redshift evolution} in the sizes of structures.
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

We use the 2pCF across the LOS as a statistical tool to probe the volume effect.
The galaxy 2pCF as a function of galaxy separation perpendicular to the LOS, $\xi(r_\perp)$, is computed for snapshot data of mock galaxies at redshifts 0.5, 1, 1.5 and 2.
We adopt the Landy-Szalay estimator~\citep{1993ApJ...412...64L},
\begin{equation}
\xi(r_\perp)=\frac{DD-2DR+RR}{RR}\ ,
\end{equation}
where $DD$ is the number of galaxy--galaxy pairs, 
$DR$ the number of galaxy-random pairs, 
and $RR$ is the number of random--random pairs, 
all separated by a distance defined by $r_\perp\pm\Delta_{r_\perp}$ where we choose $\Delta_{r_\perp}=1h^{-1}\rm Mpc$.
The random catalogue consists of unclustered points uniformly distributed in the same space as the simulated data. 
In an effort to reduce the statistical variance of the estimator, we use 50 times as many random points as we have galaxies.

@@

\subsection{Galaxy 2pCF across the LOS: at different redshifts}\label{sec_2pCF_diffz}

\begin{figure*}
   \centering{
%   \includegraphics[width=18cm]{fig9_0.eps}
%   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
 %   \includegraphics[width=18cm]{fig3.eps}
%    \includegraphics[width=18cm]{fig3_b.eps}
    \includegraphics[width=2\columnwidth]{fig3.eps}
    \includegraphics[width=2\columnwidth]{fig3_b.eps}
   }
   \caption{\label{fig_diffz}
  The 2pCF across the LOS, $\xi_{r_\perp}$ (left panels), the shape of $\hat{\xi}_{r_\perp}$ (middle panels),
  and the evolution with respect to the $z=0$ value, $\hat{\xi}_{r_{\perp}}(z=z_i) - \hat{\xi}_{r_{\perp}}(z=0)$ (right panels). 
  Upper panels show that in the correct cosmology the redshift evolution of the shape of 2pCF is rather small regardless of the large redshift evolution of the amplitude, 
  whereas the lower panels show that, in a wrong cosmology $\Omega_m = 0.05,w=-1.5$, the redshift evolution of $\hat{\xi}_{r_\perp}$ is very significant.
   }
\end{figure*}

The upper-left panel of Figure \ref{fig_diffz} displays the 2pCF across the LOS measured from HR4 mock galaxies. % (multiplied by scale $r$) in the five snapshot.
We multiply $\xi$ by the separation $r_\perp$ to obtain similar statistical uncertainty on all scales.
For convenience we will use the denotation
\begin{equation}
 \xi_{r_{\perp}} \equiv r_{\perp} \xi.
\end{equation}

@@

In the upper-middle panel, the overlapping of $\hat\xi_{r_{\perp}}$
clearly shows that there is minimal redshift evolution of the shape.
In the upper-right panel, 
we further show the residual evolution at high redshifts 
with respect to $z=0$.
There is only 1-4\% enhancement 
at $r<10h^{-1}\rm Mpc$,
and $<1.5\%$ suppression at $r>25 h^{-1}\rm Mpc$.
The trend is monotonic with redshift.

@@

\subsection{Galaxy 2pCF across the LOS: cosmological effect }

The 2pCF across the LOS for galaxy positions constructed in a wrongly assumed cosmology $\Omega_m=0.05,\ w=-1.5$
is displayed in the lower panels of Figure \ref{fig_diffz}.
The scaling uniformly shifts the clustering pattern on all scales, 
leading to a biased $\hat \xi_{r_\perp}$, which is 
related with the true $\hat \xi$ as
\begin{equation}
 \hat \xi_{r_\perp,\rm wrong}(r) = \hat \xi_{r_\perp, \rm correct}(\alpha_{\perp} r),
\end{equation}
a simple consequence of the fact that the clustering pattern at scale $r$ is rescaled to $\alpha_{\perp} r$.

@@

This scaling not only changes the shape of the 2pCF but also changes the value of $ \xi_{r_\perp}$. %The amplitude of $r_\perp\xi$ is amplified due to the stretch of scale.
As is shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
the higher the redshift, the greater the enhancement
\footnote{The value of $\xi$ is not affected by the mis-scaling. 
But since we are using $r_\perp\xi$ rather than $\xi$, the y-axis values are affected. 
For a 20\% up-rescaling, the peak value of $r_\perp\xi$ is also increased by 20\%.}.%the amplitude monotonically increases as a function of redshift.

@@

The galaxy peculiar velocity contaminates the observed redshift and distorts 
the inferred galaxy radial position.
It was the major systematic in our previous works \citep{Li2014,Li2015,Li2016}
of statistical analysis on the 3D galaxy distribution.

The effect of RSD is much milder in this work. 
The angular positions of galaxies are not shifted by RSD at all;
the only effect of RSD enter in the redshift distribution of the galaxies in our predefined redshift shell.
The galaxies observed in a survey are split into shells of subsamples, 
with different redshift ranges. This allows us to obtain 2pCF measurement at various redshifts.
RSD distorts the galaxy redshift and as a result some galaxies 
(especially those close to the boundaries of shells) are assigned to the wrong redshift shells.

@@

We vary the mass cut and check the effect of galaxy bias on $\hat \xi_{r_\perp}$.
The second row of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3150\times3150\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
Four values of minimal mass limits, $3\times 10^{11} M_{\odot}$, $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$,
are imposed to create samples with different galaxy biases.
The measured 2pCF across the LOS are displayed.
